Figures to insert in text

### 2018-03-14 Chapters/Chapter02.tex
SDM Conclusion

\begin{flushright}{\slshape
    {Pentti Kanerva's memory model was a revelation for me: \\
    it was the very first piece of research I had ever come across\\
    that made me feel I could glimpse the distant goal of understanding \\
    how the brain works as a whole. It gave me a concrete sense for\\
    how familiar mental phenomena could be thought of as distributed\\
    patterns of micro-events, thanks to beautiful mathematics.} \\ \medskip
    --- Douglas Hofstadter
    \bigskip
    \bigskip

    {How is memory gradually built up during one's conscious, or\\
    even unconscious, life and thought?  My guess is that everything \\
    we experience is classified and registered on very many parallel \\
    channels in different locations} \\ \medskip
    --- Stanislaw Ulam}
\end{flushright}
\bigskip
\bigskip

@@

% \subsection{i versus l}

@@

\section{Symmetrical, rapidly accessible, Hard Locations}

>>>>

\begin{flushright}{\slshape
    {Before I came across it, I had read many articles describing intricate properties of neurons, the many varieties of neurotransmitters and second-messenger molecules, synaptic modification processes, complex and hypercomplex cells, columns in the visual cortex, and so on.  All of this was fascinating but seemed very biological and microscopic:  altogether quite distant from everyday mental experiences.  I simply had never come across a cogent theory that addressed brain mechanisms on a global level.  Pentti Kanerva's memory model was a revelation for me: it was the very first piece of research I had ever come across that made me feel I could glimpse the distant goal of understanding how the brain works as a whole. It gave me a concrete sense for how familiar mental phenomena could be thought of as distributed patterns of micro-events, thanks to beautiful mathematics.} \\ \medskip
    --- Douglas Hofstadter}
\end{flushright}
\bigskip
\bigskip

@@

\section{``i'' versus ``l'' issue}

The classification algorithm had some problems classifying the letter ``i'' and ``l''. It may have happened because their distance is not enough. In this case, SDM could not differenciate the details --- it has only considered the big picture. Although this behavior is close to how we see things, we also have the ability to zoom and focus in the details, discerning letter ``i'' from letter ``l''.

I have run the classification algorithm under the MNIST database of handwritten digits \citep{deng2012mnist}. First, SDM has been trained with the 60,000 training images, and then it classified the 10,000 testing images. It has given the correct classification for 77.22\% of the images, which is inferior to the specialized algorithms. For instance, in 1998, \citet{lecun1998gradient} has developed algorithms which reaches from 88\%, using linear classifier, to 99.7\%, using convolutional net. For a review of the algorithms' performance in the MNIST database, see \cite{mnist}.

Looking into the reason behind images incorrectly classified, I have found that the issue is very related to the ``i'' versus ``l'' issue. Some handwritten digits are very close to others, and a ``2'' or a ``7'' may look like a ``1'', for instance. So, how can we solve this issue without using anything specific to images? The machine learning algorithms use specific tecniques to ace performance. I would like to unveil a solution closer to how we behave, even if this leads to smaller performance.

An unexplored idea is to use other SDMs which communicates. A first SDM would write the whole picture, just like we have done. Another SDM would write specific parts of the image, just like our eye focusing in specific parts. When reading, they may compose the counters and give a more precise classification.

@@

\section{Symmetrical, rapidly accessible, hard locations}
